|

### 2024-09-04 manuscript/paperCMSACversion.Rmd
updated with dups removed.

@@

<!-- % latex table generated in R 4.2.2 by xtable 1.8-4 package -->
<!-- % Mon Feb 26 09:06:03 2024 -->
\begin{table}[ht]
\centering
\begin{tabular}{rrrrr}
  \hline
 & $\beta$ & $e^{\beta}$ & s.e. & p-value \\ 
  \hline
E-F TRUE & 0.17328 & 1.18920 & 0.28884 & 0.54856 \\ 
  GP & -0.00059 & 0.99941 & 0.00022 & 0.00815 \\ 
  Ht & -0.04484 & 0.95615 & 0.04430 & 0.31144 \\ 
  Wt & 0.02274 & 1.02300 & 0.00652 & 0.00049 \\ 
  DOB & -0.01766 & 0.98250 & 0.00821 & 0.03140 \\ 
  $I_D$ & -0.36479 & 0.69434 & 0.17428 & 0.03633 \\ 
  $I_W$ & -0.25905 & 0.77178 & 0.15869 & 0.10258 \\ 
   \hline
\end{tabular}
\caption{E-F \label{tab:EF}}
\end{table}

<!-- % latex table generated in R 4.2.2 by xtable 1.8-4 package -->
<!-- % Mon Feb 26 09:04:35 2024 -->
\begin{table}[ht]
\centering
\begin{tabular}{rrrrr}
  \hline
 & $\beta$ & $e^{\beta}$ & s.e. & p-value \\ 
  \hline
E-P TRUE & 0.83023 & 2.29385 & 0.26443 & 0.00169 \\ 
  GP & -0.00051 & 0.99949 & 0.00021 & 0.01759 \\ 
  Ht & -0.03859 & 0.96215 & 0.04406 & 0.38111 \\ 
  Wt & 0.02001 & 1.02022 & 0.00654 & 0.00221 \\ 
  DOB & -0.01778 & 0.98238 & 0.00827 & 0.03150 \\ 
  $I_D$ & -0.36900 & 0.69142 & 0.17444 & 0.03440 \\ 
  $I_W$ & -0.28804 & 0.74973 & 0.15946 & 0.07087 \\ 
   \hline
   \hline
\end{tabular}
\caption{E-P \label{tab:EP}}
\end{table}

@@

# Conclusion {#sec:conclusion}

>>>>

#dat <- dat[!duplicated(dat$Player),] #6005 obs left

@@

<!-- % latex table generated in R 4.2.2 by xtable 1.8-4 package -->
<!-- % Sep 4  2024 -->
\begin{table}[ht]
\centering
\begin{tabular}{rrrrr}
  \hline
 & $\beta$ & $e^{\beta}$ & s.e. & p-value \\ 
  \hline
  EFTRUE & 0.19994 & 1.22132 & 0.28948 & 0.48977 \\ 
  GP.x & -0.00061 & 0.99939 & 0.00023 & 0.00675 \\ 
  Ht & -0.03414 & 0.96644 & 0.04465 & 0.44455 \\ 
  Wt & 0.02134 & 1.02157 & 0.00658 & 0.00118 \\ 
  DOB.Year & -0.01691 & 0.98323 & 0.00825 & 0.04047 \\ 
  Pos2D & -0.38403 & 0.68111 & 0.17532 & 0.02849 \\ 
  Pos2W & -0.28394 & 0.75281 & 0.15967 & 0.07536 \\ 
   \hline
\end{tabular}
\caption{E-F \label{tab:EF}}
\end{table}

<!-- % latex table generated in R 4.2.2 by xtable 1.8-4 package -->
<!-- % Mon Feb 26 09:04:35 2024 -->
\begin{table}[ht]
\centering
\begin{tabular}{rrrrr}
  \hline
 & $\beta$ & $e^{\beta}$ & s.e. & p-value \\ 
  \hline
EPTRUE & 0.85436 & 2.34988 & 0.26474 & 0.00125 \\ 
  GP.x & -0.00052 & 0.99948 & 0.00022 & 0.01587 \\ 
  Ht & -0.02783 & 0.97255 & 0.04439 & 0.53069 \\ 
  Wt & 0.01859 & 1.01877 & 0.00659 & 0.00480 \\ 
  DOB.Year & -0.01699 & 0.98316 & 0.00831 & 0.04102 \\ 
  $I_D$ & -0.38847 & 0.67810 & 0.17549 & 0.02686 \\ 
  $I_W$ & -0.31332 & 0.73102 & 0.16048 & 0.05089 \\ 
   \hline
   \hline
\end{tabular}
\caption{E-P \label{tab:EP}}
\end{table}

@@

# Conclusion {#sec:conclusion}
@Popkin2023 presented work looking for differences in mortality rates between NHL enforcers and non-enforcers who played between 1967 and 2022 where they defined enforcers in two ways: one based on the number of career fights and the other based on the average career penalty minutes per game.  They performed a matched-cohort study matching on date of birth, total number of games played, height, weight, and position.  They conclude there there is no statistically significant difference in the mortality rates for either definition of enforcer.  They then go on to perform an additional analytics where they condition on death and show that of players in their matched data set who are deceased, enforcers, using either definition, died an average of about 10 years earlier than their non-enforcer counterparts.

 <!-- including date of birth, total number of games played, height, weight, and position played. -->
